---
title: "R practice"
output: html_document
author: "Onpreeya Phetchpitak"
---

# Necessary Libraries

```{r}
library(swirl)
```

# **Fundamentals of R**

## Swirl Tutorial

```{r}
# swirl()
```

## Exercise 1

```{r}
sum(2000:20000)
```

## Exercise 2

```{r}
a <- 5
b <- 2:20
a
b
```

> a is an object assigned to 5 (numeric value). b is a vector object with values from 2 to 20 with 1 incremental (i.e., 2, 3, 4, 5, ..., 20). Then the last 2 lines are to print the values of a and b objects.

## Exercise 3

```{r}
a+b
sum(a,b)
```

The results are different; a+b is to add a (which is 5) to each of the b but sum(a,b) is adding all single numeric objects into one value.

## Exercise 4

```{r}
# What is the sum of the 5th through 10th element of object b? Provide your code and the sum.

sum(b[5:10])
```

## Exercise 5

```{r}
# What is the sum of the 3rd, 8th, and 10th element of b?
sum(b[c(3,8,10)])
```

## Exercise 6

```{r}
m <- matrix(data=1:25,ncol=5,byrow=T)
m
m[5,5]
```

```{r}
m[3,]

m[,3:5]
```

When extracting from a 2-dimensional object, which number specifies rows and which specifies columns?

> The first one is row and the latter one is column

What does `m[3,]` do?

> Print all columns in the third row.

How can you extract the 3rd, 4th and 5th columns of m together as one object? `m[,3:5]`

```{r}
cbind(m,101:105)
```

## Exercise 7

What does the cbind command do?

> Adding a new column into an existing matrix

How about rbind?

> Adding a new row into an existing matrix

Create a new object “n” where the first row is a new row of numbers (your choice) and the following rows are the rows from matrix m. Optional: do the same but reverse the order of the rows from matrix m.

```{r}
n <- rbind(-5:-1,m)
n
```
